---
title: "Data Health Report"
output: html_document
---
# QDQE Report Visualizer Tool 
```{r, echo=FALSE}
options(warn=-1)     #suppress warnings

rdata_file <- "reporting_variables.RData"
data_loaded <- load(paste(getwd(),"/",rdata_file,sep=""))

num_enablement_config <- sum(count_da_category[c("Enablement/Configuration Issue","Failed/Incomplete Validation")])


count_status          <- margin.table(da_status_by_issue,2)
sum_unuable_reg       <- sum(count_status[names(count_status)%in%c("Awaiting Data", "Preliminary - Major Anomalies")])
sum_total_reg         <- sum(count_status)

count_status           <- margin.table(sum_MW_by_status,2)
sum_unuable_mw         <- sum(count_status[names(count_status)%in%c("Awaiting Data", "Preliminary - Major Anomalies")])
sum_total_mw           <- sum(count_status)
pct_unusable_mw        <-sum_unuable_mw/sum_total_mw

bulk_issues_table <- bulk_issues_table[!is.na(names(bulk_issues_table))]

```

Team,
In the recent dispatch, `r round(pct_unusable_mw*100,2)`% of our portfolio's MW (`r sum_unuable_reg` of `r sum_total_reg` assets) were unusable for initial performance calculations. `r round(num_enablement_config/sum_unuable_reg*100,2)`% of these issues (`r num_enablement_config`/`r sum_unuable_reg` assets) resulted from incomplete enablement, incorrect platform configuration, or unfinished DMT meter validations. The majority of the remaining assets had no data available in the platform for the M&V period.<link href="custom.css" rel="stylesheet"> 
 
## The following table describes the sources of reduced visibility:

```{r results='asis', echo=FALSE, fig.width=8}
#print table 
library(xtable)

df_da_category <- data.frame("Category"=names(count_da_category),
              "Number Not Reporting"=as.integer(unname(count_da_category)),
                             "Percent Not Reporting"=paste(as.integer(100*unname(count_da_category)/(count_da_category[names(count_da_category)=="Total"])),"%",sep=""),
                                "Description"=c("EnerNOC platform is not capturing entire utility service account",
                                                "Data is missing for most or all of M&V period",
                                                "Open 2012/2013 validation case",
                                                "Anomalous estimations, anomalous zeroes, spikes, drops",
                                                ""),
                                "Issue Owner"=c("Ops",
                                                "Ops",
                                                "DMT",
                                                "Ops,PS&T",
                                                ""))

df_da_category<-df_da_category[order(-df_da_category$Number.Not.Reporting),]

df_da_category_total<-df_da_category[df_da_category$Category %in% c("Total"),]
df_da_category<-df_da_category[!df_da_category$Category %in% c("Total"),]
df_da_category<-df_da_category[!df_da_category$Number.Not.Reporting %in% 0,]
df_da_category<-rbind(df_da_category,df_da_category_total)

summary_table <- xtable(data.frame(df_da_category))
print.xtable(summary_table,type="html",include.rownames=FALSE)
#print(summary_table, include.rownames=FALSE, scalebox=0.7)  #generate a table for pdf output
```
*Further details into impacted assets are available from the Data Quality team

## Graphs
```{r results='asis', echo=FALSE, fig.width=12}
#print barplot 1
barplot(da_status_by_issue, main="DA data status by registration issue",
  xlab="DA Data Status", 
  ylab="Number of registrations",
    legend = rownames(da_status_by_issue))

#barplot with number of bulk issues
if(length(bulk_issues_table)!=0){            #if bulk issues exist, plot them here
  barplot(bulk_issues_table, main="Bulk Issues",
          xlab="", 
          ylab="Number of registrations")
  }

#create contingency table with expected capacity sums
p <- barplot(sum_MW_by_status, main="",
             xlab="DA Data Status",
             ylab="Expected Capacity (MW)",
             legend = rownames(sum_MW_by_status)) 

```
